FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-12 NewVersion/sections/Formalization.tex
small fix S3

The second condition of \textsc{(T-Intf)} is more complex, and is the key to type soundness. Unlike C++ which rejects on ambiguous calls,
\MIM{} rejects on the definition of interfaces when they reach a diamond. Consider the case when the second condition is broken: $\mbody(m, J, J)$
is defined but $\mbody(m, I, J)$ is undefined for some $J$ and $m$. This indicates that $m$ is available and unambiguous from the perspective of $J$,
but is ambiguous to $I$ on branch $J$. That means that there are multiple overriding paths of $m$ from $J$ to $I$, which form a diamond. Hence rejecting
that case meets our expectation.

@@

\paragraph{Example} \bruno{what is the purpose of this example:
  state-it upfront please. Is this example meant to ilustrate T-Inf?
  Then it's better to have the example together with the text
  explaining T-inf.}
Here we refer to case (e)
in Figure~\ref{fig:examplesmbody}. To be specific, the entire program in \MIM{} is as follows:

\vspace{3pt}\begin{lstlisting}
interface T                 {}
interface T1 extends T      {}
interface T2 extends T      {}
interface A                 { T m() override A { return new T(); } }
interface B extends A       { T m() override A { return new T1(); } }
interface C extends A       { T m() override A { return new T2(); } }
interface D extends B, C {}

\begin{figure*}[t]
\saveSpaceFig

\begin{mathpar}
	\framebox{$ I <: J $} \hspace{.5in} \subid \\
	\subtrans \hspace{.5in} \subextends \\

>>>>

The second condition of \textsc{(T-Intf)} is more complex, and is the key to type soundness. Unlike C++ which rejects on ambiguous calls,
\MIM{} rejects on the definition of interfaces when they reach a diamond. Consider the case when the second condition is broken: $\mbody(m, J, J)$
is defined but $\mbody(m, I, J)$ is undefined for some $J$ and $m$. This indicates that $m$ is available and unambiguous from the perspective of $J$,
but is ambiguous to $I$ on branch $J$. That means that there are multiple overriding paths of $m$ from $J$ to $I$, which form a diamond. Hence rejecting
that case meets our expectation. Below is an example (Figure~\ref{fig:examplesmbody} (e)) that illustrates the reason why this condition is needed:
\bruno{what is the purpose of this example:
  state-it upfront please. Is this example meant to ilustrate T-Inf?
  Then it's better to have the example together with the text
  explaining T-inf.} \yanlin{revised.please check whether you're happy with it.}
\vspace{3pt}\begin{lstlisting}
interface T                 {}
interface T1 extends T      {}
interface T2 extends T      {}
interface A                 { T m() override A { return new T(); } }
interface B extends A       { T m() override A { return new T1(); } }
interface C extends A       { T m() override A { return new T2(); } }
interface D extends B, C {}

@@

\begin{figure*}[t]
\saveSpaceFig
\begin{mathpar}
	\framebox{$ I <: J $} \hspace{.5in} \subid \\
	\subtrans \hspace{.5in} \subextends \\
